Title

### 2023-04-02 Paper/PAPER.tex
paper 11

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    \vspace{5pt}
    \textbf{Keywords}: heuristic hierarchical multiple regression, deep forest.

@@

\textbf{Problem (e) :}
\begin{itemize}
    \item Create a one-to two-page report with well-chosen graphics to assist the Hong Kong sailboat broker to understand your findings.
\end{itemize}
%我们的工作
\subsection{Our work \& Model Overview}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Model.png}
    \caption{Model Framework}\label{fig:Model}
\end{figure}

We propose a model framework as shown in Figure \ref{fig:Model}, The model takes \texttt{Year}, \texttt{Region}, \texttt{Variant} as inputs, 
, \texttt{Price} as output, and performs a heuristic hierarchical multiple regression. 
Specifically, in each regression layer, one variable is denormalized, and the other two variables are normalized. 
The obtained \texttt{Price} at this time is used as the Effect of this variable. 
At the same time, the fitting result is used as the baseline for normalization in the next layer and is involved in the regression. 
This process is iterated continuously until the model trains a precise fitting effect.

It is worth noting that we use a heuristic approach for each normalization. 
For larger datasets, we perform regression, while for smaller datasets, we take their average. 
This method greatly improves the accuracy of the model predictions.
\section{Assumptions and Justififications}
% 问题假设
\subsection{Assumptions}
To simplify our problems, we make the following basic assumptions, each of which is
adequately justified.
\begin{itemize}
    \item The price of used sailboats is solely determined by the factors in the dataset.
    \item The factors in the dataset are independent and unrelated.
    \item The data in the dataset are all real, reasonable, and follow a certain pattern.
    \item The pricing required by a broker should be reasonable and in accordance with market rules, rather than false pricing.
\end{itemize}
%符号含义
\subsection{Notations}
\ 
% 三线表示例
\begin{table}[!htbp]
\begin{center}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}
\end{center}
\end{table}
\section{Data Exploration}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Data.png}
    \caption{Data Exploration}\label{fig:Data}
\end{figure}

@@

\subsection{Data Analysis}

@@

\section{The Prediction Model of Used Sailboat Prices}
\subsection{The Establishment of The Model}

\subsection{Model Validation}
\subsection{Model Accuracy Analysis}

>>>>

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    \vspace{5pt}
    \textbf{Keywords}:  Linear interpolation, Adaptive Density-Based Clustering, Heuristic Hierarchical Multiple Regression, Deep Forest Model,  Machine Learning, Data Mining, Analysis of Variance.

@@

\textbf{Problem (e) :}
\begin{itemize}
    \item Create a one-to two-page report with well-chosen graphics to assist the Hong Kong sailboat broker to understand your findings.
\end{itemize}
%我们的工作
\subsection{Our work \& Model Overview}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{OurWork.png}
    \caption{Model Framework}\label{fig:OurWork}
\end{figure}

\section{Assumptions and Justifications}
% 问题假设
\subsection{Assumptions}
To simplify our problems, we make the following basic assumptions, each of which is
adequately justified.
\begin{itemize}
    \item The price of used sailboats is solely determined by the factors in the dataset.
    \item The factors in the dataset are independent and unrelated.
    \item The data in the dataset are all real, reasonable, and follow a certain pattern.
    \item The pricing required by a broker should be reasonable and in accordance with market rules, rather than false pricing.
\end{itemize}
%符号含义
\subsection{Notations}
\ 
% 三线表示例
\begin{table}[!htbp]
\begin{center}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}
\end{center}
\end{table}
\section{Data Exploration}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Data.png}
    \caption{Data Exploration}\label{fig:Data}
\end{figure}

@@

@@

\subsection{Data Analysis}
There are lots of labels related to specifications, 
and it is hard for us to discuss their influence on listing price one by one. 
However, trying to directly preform regression based on these labels by machine learning models can cause \textbf{overfitting issues}.
Nevertheless, we can still draw some relatively simple conclusions from the data, which provide theoretical support for our subsequent modeling:
\begin{itemize}
    \item Time: Time is a quasi-continuous and ordered variable, 
    and the price has an obvious linear relationship with time.(see Figure \ref{fig:year_price} and Table \ref{table: correlation_coefficient})
    \item Variant and Region: They are obviously related to the price, but due to their unordered and non-continuous nature, further analysis is needed.
\end{itemize}
\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{monohulled_price_year.png}
    \caption{Monohulled}\label{subfig:mono_year}
    \end{subfigure}
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{catamaran_price_year.png}
    \caption{Catamaran}\label{subfig:cata_year}
    \end{subfigure}
    \caption{The relationship between year and price}\label{fig:year_price}
\end{figure}

\begin{table}[h!]
    \begin{center}
      \begin{tabular}{c|c|c|c}
        & Pearson & Spearman & Kendall\\
        \hline
        \hline
        Monohulled &0.964 & 0.989 & 0.943 \\
        Catamaran  &0.960& 0.971 & 0.867\\
      \end{tabular}
      \caption{The correlation coefficient of year and price}\label{table: correlation_coefficient}
    \end{center}
\end{table}

\section{The Prediction Model of Used Sailboat Prices}

\subsection{The Establishment of The Model}
\subsubsection{Model 1 \textemdash  Heuristic Hierarchical Multiple Regression}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Model1.png}
    \caption{Brief process of Model 1}\label{fig:Model1}
\end{figure}
We propose \emph{Model 1} as shown in Figure \ref{fig:Model1}, The model takes \texttt{Year}, \texttt{Region}, \texttt{Variant} as inputs, 
, \texttt{Price} as output, and performs a heuristic hierarchical multiple regression. 
Specifically, in each regression layer, one variable is denormalized, and the other two variables are normalized. 
The obtained \texttt{Price} at this time is used as the Effect of this variable. 
At the same time, the fitting result is used as the baseline for normalization in the next layer and is involved in the regression. 
This process is iterated continuously until the model trains a precise fitting effect.

It is worth noting that we use a heuristic approach for each normalization. 
For larger datasets, we perform regression, while for smaller datasets, we take their average. 
This method greatly improves the accuracy of the model predictions.
\subsubsection{Model 2 \textemdash  Deep Forest Model}
However, \emph{Model 1} is somehow incomplete because \emph{Model 1} requires that the variant and region of the predicted data have appeared in the dataset before. 
However, in actual prediction, the variant and region may be opaque to the model. 
Taking the third question as an example, \emph{Model 1} can't predict the price of Hong Kong because the region effect of Hong Kong hasn't been evaluated by the model. 
Therefore, we use the \textbf{Deep Forest Model} to establish \emph{Model 2}.

Decision tree is a common machine learning method with two models: classification and regression. 
At the beginning, we used the basic decision tree for regression, but the model error was large, 
and the accuracy for price prediction was poor. 
Therefore, we optimized the model using the deep forest algorithm. 
Deep forest is an ensemble learning model based on random forest. 
Unlike traditional decision trees, deep forest trains each tree classifier with a randomized strategy to increase the diversity of the model.
Compared with a single decision tree, the deep forest model is more robust.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Deep_forest.png}
    \caption{Deep Forest Model}\label{fig:DF}
\end{figure}

As for \emph{Model 2}, we first expanded the dataset to obtain quantified data for regions and variants.
Specifically, for variants, we expanded data such as \texttt{draft}, \texttt{beam}, \texttt{water tank}, \texttt{fuel tank}, \texttt{cabins}, \texttt{displacement}, etc. 
For regions, we expanded data such as \texttt{GDP}, \texttt{Gini coefficient}, \texttt{Human Development Index}, etc. 
When dealing with unmarked variants and regions, we first used \emph{Model 1} to obtain the effects of marked variants and regions, and then applied the effects of marked variants and regions to the deep forest. 
By expanding the data for regression, we obtained the effects of unmarked variants and regions, and thus predicted the price.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Model2.png}
    \caption{Brief process of Model 2}\label{fig:Model2}
\end{figure}

\subsection{Model Validation}

\subsection{Model Accuracy Analysis}
Due to the limited data provided for some sailship types, 
they belong to imbalanced datasets. 
Therefore, we need to use as much data as possible for training to prevent the loss of small-sample data during training. 
Given that the leave-one-out method is not affected by random partition, 
it is effective for small-sample and imbalanced datasets, 
and can accurately evaluate the performance of the model, 
we used the \textbf{leave-one-out method} to analyze the model's error in the error analysis part, 
and adopted mean squared error as the performance measure of the model.

Given a set of examples in a prediction task $D=\{(\textbf{x}_1,y_1),(\textbf{x}_2,y_2) ,\cdots,(\textbf{x}_m,y_m)  \}$, 
In which $y_i$ represents the true label of sample $\textbf{x}_i$, 
and mean squared error is represented as:
$$E(f;D)=\frac{1}{m}\sum_{i=1}^{m}(f(\textbf{x}_i)-y_i)^2$$
